\documentclass{resume}
\usepackage[left=0.6in,top=0.6in,right=0.6in,bottom=0.6in]{geometry}
\usepackage[svgnames]{xcolor}
\usepackage{hyperref}
\hypersetup{%
  colorlinks=true,          % hyperlinks
  allcolors=DarkRed,%
  pdfborderstyle={/S/U/W 1} % border style will be underline of width 1pt
}

\usepackage{vwcol}
\usepackage{natbib}
\usepackage{cfr-lm}         % make old style numbers default
\usepackage{graphicx}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% TITLE SECTION
\begin{center}
    \name{Alice Alice}
    \contact
        {999$\cdot$999$\cdot$9999}
        {\href{mailto://alice@spaceship.com}{alice@spaceship.com}}
        {\href{https://alice.ship}{alice.ship}}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% EDUCATION 
\section{Education} 
\begin{content}
    {\bf Einstein Labs} {M.Sc. Inertial Frames} \hfill {\bf 2021 --} 

    {\bf Lorentz Institution} \hfill {\bf 2017 -- 2020} \\ 
    {B.Sc. Time Dilation {\em\&} Length Contraction, Minor Simultaneity} \hfill 
    {\em CGPA: \textpl{4.0/4.0} \quad Dean's List}
    
    % \vspace{-.25\baselineskip}
    % {\em Honours:} If you'd rather list your awards here than in a separate section later, simply write the awards here and comment out that section (and vice versa).
\sectionlineskip
\end{content}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% RESEARCH EXPERIENCE
\section{Research Experience}
\begin{content}

    \begin{position}{Relativity Research Group}{May 2020 -- present}{Research intern}{Prof.~Hermann Minkowski}{Institution}
    \item Participated in experiments involving travelling at very high speeds holding clocks and rulers.
    \item This is an environment for your positions with 5 fields: research group or topic, date, position name, professor or group, institution. 
    \end{position}
    \vspace{-.5\baselineskip}
    Here's a little comment after a position if you want one (not really recommended).

    \begin{position}{Bathtub Labs}{January 2021 -- present}{Junior Tree Researcher}{}{}
    \item If you want to remove the second line (professor and institution), simply leave those two fields empty. 
    \end{position}

\sectionlineskip
\end{content}
\vspace{-3\medskipamount}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PUBLICATIONS 
\noindent
\renewcommand{\refname}{Publications}   % name of the reference section
\bibliography{biblio.bib}               % bib file
\bibliographystyle{abbrvnat}            % citation style
\nocite{*}
\sectionlineskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% AWARDS
\section{Awards} 
\begin{content}
    \prize[s]{1\textsuperscript{st} place, A Short Prize}{2020}{has its description on the same line and the option is toggled with \texttt{[s]}.}
    
    \prize{A Scholarship with a Longer Name}{2020, 2021}{This is the default option and has its description on a separate line. Add as many of these as you would like.}
\sectionlineskip
\end{content}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PROJECTS
\section{Projects \textbf{\em\&} Extracurriculars} 
\begin{content}
    
    \begin{position}{Einstein Institution}{August 1978 -- present}{Experimenter}{}{}
        \item Stood in many elevators careening towards earth, and travelled into the event horizon of black holes. 
        \item Further mastered holding clocks and rulers.
    \end{position}
    
    \begin{position}{Seminars on Relativity in Space}{Sept. 2020 -- Jan. 2021}{Organizer}{}{}
    \item Organizing the 2021 edition of the conference, hosted on a spaceship travelling at .9 of the speed of light.
    \end{position}
    
    \begin{position}{Lorentzian Geometry}{Summer 2020}{\normalfont\href{https://alice.ship/lorentz}{\texttt{alice.ship/lorentz}}}{}{}
    \item A project description on its own line so that it can be pretty long, though I can't think of what to write here.  
    \end{position}
    
    {\bf Very Simple Project} \enspace {\href{https://alice.ship/lorentz}{\texttt{alice.ship/lorentz}} 
    {\em A really simple entry with inline description} }
    \hfill {\bf 2018 -- present}

\sectionlineskip    
\end{content}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% TECHNICAL SKILLS
\section{Technical Skills}
\begin{content}
    \begin{tabular}{ @{} >{\bf}l @{\hspace{6ex}} l }
        Programming Languages & Python, \LaTeX\ {\em \&} \TeX \\
        Tools \textbf{\em\&} Technologies & Spaceship steering \\
        Languages & Earth languages
    \end{tabular}
\sectionlineskip
\end{content}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% COURSE WORK
\section{Selected Course Work}
\begin{tabular}{l l l}
        \qquad {\bf Mathematics} & \qquad {\bf Physics} & \qquad {\bf Computer Science} \\[.5\smallskipamount]
        
        Analysis Sequence & Classical {\em\&} Quantum Mechanics & H. Algorithms {\em \&} Data Structures \\ 
        Complex Analysis & Thermal {\em \&} Statistical Physics & Mathematical Foundations of Machine Learning \\
        Abstract  Algebra & General Relativity & Reinforcement Learning \\
        Cryptography &  Quantum Field Theory & Probabilistic Analysis of Algorithms 
\end{tabular}

\end{document}
