\documentclass{resume}
% showframe
\usepackage[left=0.6in,top=0.6in,right=0.6in,bottom=0.55in]{geometry}
\usepackage{vwcol}
\usepackage{cfr-lm}  % make old style numbers default
% \usepackage{apacite} % citations in APA style
\usepackage{natbib}
\setlength{\bibsep}{2.5pt}
\usepackage[svgnames]{xcolor}
\usepackage{hyperref}
\hypersetup{%
  colorlinks=true,% hyperlinks
  allcolors=DarkRed,%
  pdfborderstyle={/S/U/W 1}% border style will be underline of width 1pt
}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% TITLE
\begin{center}
    \name{Bob Bob}
    \contact
        {999$\cdot$999$\cdot$9999}
        {\href{mailto://bob@spaceship.com}{bob@spaceship.com}}
        {\href{https://bob.ship}{bob.ship}}
\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% EDUCATION
\section{Education} 
\begin{content}
    {\bf Einstein Labs} {M.Sc. Inertial Frames} \hfill {\bf 2021 --} 

    {\bf Lorentz Institution} \hfill {\bf 2017 -- 2020} \\ 
    {B.Sc. Time Dilation {\em\&} Length Contraction, Minor Simultaneity} \hfill 
    {\em CGPA: \textpl{4.0/4.0} \quad Dean's List}
    
    \vspace{-.25\baselineskip}
    
    {\em Honours:} For the short version of the template, it's better to write your awards here.
    
    {\bf \em Technical skills:} Python {\footnotesize (numpy, tensorflow, matplotlib, pandas)}, Java, HTML/CSS, JavaScript (p5.js), C, \LaTeX; Bash, Git; Adobe Photoshop {\em \&} Illustrator, GIMP; Blender.
\sectionlineskip
\end{content}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% RESEARCH EXPERIENCE
\section{Research Experience}
\begin{content}

    \begin{position}{Relativity Research Group}{May 2020 -- present}{Research intern}{Prof.~Hermann Minkowski}{Institution}
    \item Participated in experiments involving travelling at very high speeds holding clocks and rulers.
    \item This is an environment for your positions with 5 fields: research group or topic, date, position name, professor or group, institution. 
    \end{position}
    \vspace{-.5\baselineskip}
    Here's a little comment after a position if you want one (not really recommended).

    \begin{position}{Bathtub Labs}{January 2021 -- present}{Junior Tree Researcher}{}{}
    \item If you want to remove the second line (professor and institution), simply leave those two fields empty. 
    \end{position}

\sectionlineskip
\end{content}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% FIRST COLUMN 
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\noindent 
\begin{minipage}[t]{.41\textwidth} \vspace{0pt}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PUBLICATIONS
\renewcommand{\refname}{Publications}
\bibliography{bibshort}
\bibliographystyle{abbrvnat}
\nocite{*}
\sectionlineskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% AWARDS
\section{Awards}
    \prize{A short prize}{2019, 2020}{If you have space to add this section here, after each prize you need to add a \textbackslash \texttt{medskip} after for spacing.}
    \medskip
    
    \prize{A prize}{2019}{Another description.}
    
\sectionlineskip

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% SECOND COLUMN
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{minipage}
\hfill 
\begin{minipage}[t]{.57\textwidth} 
\vspace{0pt} %important vspace to align at the top! don't delete
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PROJECTS
\subsection{Technical Projects} 
\begin{content}
    \begin{project}{Einstein Institution}{August 1978 -- present}
        \item Stood in many elevators careening towards earth, and travelled into the event horizon of black holes. 
        \item Further mastered holding clocks and rulers.
    \end{project}
    
    \begin{project}{Seminars on Relativity in Space}{Sept. 2020 -- Jan. 2021}
    \item Organizing the 2021 edition of the conference, hosted on a spaceship travelling at .9 of the speed of light.
    \end{project}
    
    \begin{project}{Lorentzian Geometry}{\normalfont\href{https://bob.ship/lorentz}{\texttt{bob.ship/lorentz}}}
    \item A project description on its own line so that it can be pretty long, though I can't think of what to write here.  
    \end{project}
    
\end{content}
\end{minipage}


\end{document}
